Flowchart of Current Algorithm

### 2009-05-18 docs/flowchart/flowchart.tex
got rid of correct base shorthand and just put the average calls in

\item {\bf Correct Base}$[\rho_0^{\inp}, \rho^{\inp}] \rightarrow [\rho_0^{\outp}]$
is the process by which we adjust the base state density to account for
large-scale mixing.  It is also used to reset the base state enthalpy to be
the average of the full state enthalpy since we do not need to compute the complete
evolution of the base state enthalpy.
Unlike paper III where we used $\nabla\cdot\etarho$ as an adjustment to $\rho_0$, 
we instead simply set $\rho_0=\overline{\rho}$, which is analytically equivalent.
\begin{description}
\item[planar:] Set $\rho_0^{\outp} = {\bf Avg}(\rho^{\inp})$.
\item[spherical:] Set $\rho_0^{\outp} = \rho_0^{\inp} + {\bf Avg}(\rho^{\inp} - \rho_0^{\inp})$.
\end{description}

@@

\item {\bf Correct Base}$[(\rho h)_0^{n},(\rho h)^{(1)}] \rightarrow [(\rho h)_0^{n}]$.
This sets $(\rho h)_0$ to be the lateral average of $(\rho h)^{(1)}$

@@

\item {\bf Correct Base}$[\rho_0^{(2a),\star},\rho^{(2),\star}] \rightarrow [\rho_0^{n+1,\star}]$.

@@

\item {\bf Correct Base}$[\rho_0^{(2a)},\rho^{(2)}] \rightarrow [\rho_0^{n+1}]$.

>>>>

@@

\item Set $(\rho h)_0^n$ to be the lateral average of $(\rho h)^{(1)}$:
\begin{description}
\item For planar geometry, set $(\rho h)_0^n = $ {\bf Avg}$[(\rho h)^{(1)}]$
\item For spherical geometry, set $(\rho h)_0^n = (\rho h)_0^n +$ {\bf Avg}$[(\rho h)^{(1)} - (\rho h)_0^n]$
\end{description}

@@

\item Set $\rho_0^{n+1,\star}$ to be the lateral average of $\rho^{(2),\star}$:
\begin{description}
\item For planar geometry, set $\rho_0^{n+1,\star} =$ {\bf Avg}$(\rho^{(2),\star})$
\item For spherical geometry, set $\rho_0^{n+1,\star} = \rho_0^{(2a),\star} +$ {\bf Avg}$(\rho^{(2),\star} - \rho_0^{(2a),\star})$
\end{description}

@@

\item Set $\rho_0^{n+1}$ to be the lateral average of $\rho^{(2)}$:
\begin{description}
\item For planar geometry, set $\rho_0^{n+1} =$ {\bf Avg}$(\rho^{(2)})$
\item For spherical geometry, set $\rho_0^{n+1} = \rho_0^{(2a)} +$ {\bf Avg}$(\rho^{(2)} - \rho_0^{(2a)})$
\end{description}
